Incentivizing Exploration with Unbiased History

### 2018-11-02 3level.tex
,
Edits for a slightly better notation in construction.

\jmcomment{$\NG$ is also used in Lemma 3.6. We need to find another notation. And I think it should be something without subscript 2. It's generally a property of the whole construction. How about $\NG$.}

The full-disclosure paths in the first level are also split into $\NG$ disjoint subsets, called \emph{first-level groups}. Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot \NG\cdot \fdpL$ rounds in the first layer. There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$. More formally, agent $t$ is connected to the last node of each full-disclosure path in $S_1$. In other words, this agent receives message
    $m_t = \SubH{V(S_1)}$,
where $V(S_1)$ is the set of all rounds in $S_1$.
\end{construction}

>>>>

\jmcomment{$N_2$ is also used in Lemma 3.6. We need to find another notation. And I think it should be something without subscript 2. It's generally a property of the whole construction. How about $\NG$.}

The full-disclosure paths in the first level are also split into $\NG$ disjoint subsets, called \emph{first-level groups}. Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot \NG\cdot \fdpL$ rounds in the first layer. There is a 1-1 correspondence between first-level groups $G$ and second-level groups $G'$, whereby each agent in $G'$ observes the full history from the corresponding group $G$. More formally, agent in $G'$ is connected to the last node of each full-disclosure path in $G$. In other words, this agent receives message
    $\SubH{S}$,
where $S$ is the set of all rounds in $G$.
\end{construction}
